Together, Individuals Make a Difference

### 2025-01-26 论文/PAPER.tex
重命名图片

\subsection{Data Mining}
\section{Task1:}
\subsection{Details about Model 1}
The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
%带标签的方程
\begin{equation}\label{eq1}
\alpha+\beta=\gamma
\end{equation}
%不带标签的方程
\[
\alpha+\beta=\gamma
\]
$$\alpha$$

%$$ \gamma=\frac{$m_{c_{i} s_{j}}$}{$\sum m_{c_{i} s_{j}}$ }$$

%\[
%\gamma = \frac{$m_{c_i s_j}$}{$\sum m_{c_i s_j}$}
%\]
\[
\gamma = \frac{m_{c_i s_j}}{\sum m_{c_i s_j}}
\]

@@

>>>>

\subsection{Data Mining}
\subsubsection{Athlete Service Status}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=12cm]{img/Number.png}
	\caption{Number of New and Leave Athletes in Each Year}
	\label{fig:aa}
\end{figure}

% 子图（多图并列）示例，更多用法请参考 subfigure 宏包文档
% 如果您只希望几张图并列，不需要额外的 caption，那么在 figure 环境中
% 连续插入总宽度不超过 \textwidth 的多个 \includegraphics 命令即可
\begin{figure}[htbp]
	\centering
	\begin{subfigure}[b]{.5\textwidth}
		\includegraphics[width=\textwidth]{img/Times.png}
		\caption{Distribution of Serve Times}\label{subfig:left}
	\end{subfigure}
	\begin{subfigure}[b]{.5\textwidth}
		\includegraphics[width=\textwidth]{img/Years.png}
		\caption{Distribution of Serve Years}\label{subfig:right}
	\end{subfigure}
	\caption{Two images}\label{fig:subfigures}
\end{figure}

\subsubsection{Distribution of Countries' Strength Sports}

\section{Task1:}
\subsection{Medal Standings}
The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
%带标签的方程
\begin{equation}\label{eq1}
\alpha+\beta=\gamma
\end{equation}
%不带标签的方程
\[
\alpha+\beta=\gamma
\]
$$\alpha$$

\[
\gamma = \frac{m_{c_i s_j}}{\sum m_{c_i s_j}}
\]

@@

\subsection{Countries that Win Their First Medal}

\subsection{Events and Medal Counts by Countries}

\begin{figure}[htbp]
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{img/Table Tennis.png}
		\caption{Heatmap of Correlation for Table Tennis in China}\label{subfig:1}
	\end{subfigure}
	\hfill 
	\begin{subfigure}[b]{.33\textwidth}
		\includegraphics[width=\textwidth]{img/Jamaica.png}
		\caption{ Heatmap of Correlation for Athletics in Jamaica}\label{subfig:2}
	\end{subfigure}
	\hfill 
	\begin{subfigure}[b]{.32\textwidth}
		\includegraphics[width=\textwidth]{img/New Zealand.png}
		\caption{Heatmap of Correlation for Rowing in New Zealand}\label{subfig:3}
	\end{subfigure}
	\caption{Three images}\label{fig:subfigures}
\end{figure}
